Notes on Design and Implementation of Anglican

### 2015-08-19 paper/paper.tex
inference algorithms in progress

>>>>

An inference algorithm is an implementation of \texttt{infer}
multimethod from \texttt{anglican.inference} namespace. The
multimethod accepts an algorithm identifier, a query --- the
probabilistic program in which to perform the inference, an
initial value for the query, and optional algorithm parameters.

The sole purpose of the algorithm identifier is method dispatch
--- conventionally, the identifier is a keyword related to the
algorithm name (\texttt{:lmh} for Lightweight
Metropolis-Hasting, \texttt{:pcascade} for Particle Cascade
etc.). The second parameter is a query as defined by
\texttt{query} or \texttt{defquery} forms. If needed, the query
can be defined anonymously, right in the argument list of a call
to \texttt{infer}:
\begin{lstlisting}[frame=single,language=Anglican, basicstyle=\scriptsize\ttfamily, showstringspaces=false]
    (let [x 1]
      (infer :pgibbs (query (predict x)) nil))
\end{lstlisting}
A query is executed by calling the initial continuation of the
query, which accepts a value and a state. The state is supplied
by the inference algorithm, however the value is provided as a
parameter of \texttt{infer}. A query does not have to have any
parameters, in which case the value can be simply \texttt{nil}.
When a query is defined with a binding for the initial value,
the value becomes available inside the query. The value is
destructured in case of a structured binding, for example:
\begin{lstlisting}[frame=single,language=Anglican, basicstyle=\scriptsize\ttfamily, showstringspaces=false]
    (defquery my-query [mean sd]
       (predict (sample (normal mean sd))))

    (define samples (infer :lmh my-query [1.0 3.0]))
\end{lstlisting}
Finally, an indefinite number of auxiliary arguments can be
passed to \texttt{infer}. By convention, the arguments should be
keyword arguments, and are interpreted in the algorithm-specific
manner.
